---
title: "Project 2: Stat302Project2 Tutorial"
author: "Nathan Atchison"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Stat302Project2 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(magrittr)
library(randomForest)
library(ggplot2)
```


```{r}
my_penguins <- read.csv("D:/Desktop/Stat302Stuff/Projects/Project2Pipeline/Data/my_penguins.csv")
source("D:/Desktop/Stat302Stuff/Projects/Project2Pipeline/Code/my_rf_cv.R")
```

```{r}
tut_rf_mat <- matrix(data = NA, nrow = 30, ncol = 3)
tut_rf_fin_tab <- matrix(data = NA, nrow = 3, ncol = 2) 
for(i in 1:3) {
  if(i == 1) {
    curr_k <- 2
  } else if (i == 2) {
    curr_k <- 5
  } else {
    curr_k <- 10
  }
  for(j in 1:30) {
    tut_my_rf <- my_rf_cv(k = curr_k)
    tut_rf_mat[j,i] <- tut_my_rf
  }
  tut_rf_fin_tab[i,1] <- mean(tut_rf_mat[,i])
  tut_rf_fin_tab[i,2] <- sd(tut_rf_mat[,i])
}
colnames(tut_rf_fin_tab) <- c("mean", "sd")
rownames(tut_rf_fin_tab) <- c("k2", "k5", "k10")
colnames(tut_rf_mat) <- c("k2CVerr", "k5CVerr", "k10CVerr")

tut_rf_dataframe <- as.data.frame(tut_rf_mat)

tut_box1 <- ggplot2::ggplot(data = tut_rf_dataframe, ggplot2::aes(y = k2CVerr)) + ggplot2::geom_boxplot(fill = "blue")
tut_box2 <- ggplot2::ggplot(data = tut_rf_dataframe, ggplot2::aes(y = k5CVerr)) + ggplot2::geom_boxplot(fill = "red")
tut_box3 <- ggplot2::ggplot(data = tut_rf_dataframe, ggplot2::aes(y = k10CVerr)) + ggplot2::geom_boxplot(fill = "green")
ggpubr::ggarrange(tut_box1,tut_box2,tut_box3, labels = c("k=2", "k=5", "k=10"), ncol = 2, nrow = 2)
kableExtra::kable_styling(knitr::kable(tut_rf_fin_tab))
```

```{r}
ggsave(filename = "Proj2Boxplot.png", path = "D:/Desktop/Stat302Stuff/Projects/Project2Pipeline/Output/Figures")
saveRDS(object = tut_rf_fin_tab, file = "D:/Desktop/Stat302Stuff/Projects/Project2Pipeline/Output/Results/SummStatsTab.rds")
write.csv(x = tut_rf_mat, file = "D:/Desktop/Stat302Stuff/Projects/Project2Pipeline/Output/Results/SimResults.csv")
```

In the boxplots above, it seems that as the value of k increases, the range of the boxplots decreases. For example, when k = 2, we see that it has larger range from it's minimum to it's maximum when compared to k = 5 and k = 10. We also see that the range difference between k = 5 and k = 10 is smaller than the difference between k = 2 and k = 10, however, we still observe that the range is smaller for k = 10.  In the table we see that when k = 2, it has a fairly larger mean and standard deviation when it comes to k = 5 and k = 10. We also see that k = 5 and k = 10 are fairly similar in their means. However, we see that the standard deviation when k = 10 is smaller when compared to when k = 5. I think that these results are the case because as the value of k increases, we are adding more folds to the data as a whole. This means that we are taking more tests within our function. As a result of taking more tests, our results will be more accurate and as a result, our standard deviations will decrease giving us the results we received above. 
